Import_MCData

### 2024-03-18 Code/Import_MCData.Rmd
Minor edits

It tidies and organizes the data. It uses a pivot_wider and
interpolation approach to get the Actinic_par and OD values in line
rowwise. This requires careful 'arrange' of the rows. It imports a
metadata Catalog and merges the metadata with the imported data based
upon shared values for the variables 'MC', 'Tube', and 'Filename' which
should unambiguously identify a given growth trajectory measured at
OD680 or OD720.

@@

# Multiculti data files are too large to upload in a single .zip so uploaded 3 .zipped folders. Uncomment the 'DataIn' line with the folder name containing the intended files for import.   
 # DataIn <- file.path("..", "Data", "RawData", "MultiCultiData1.zip")
DataIn <- file.path("..", "Data", "RawData", "MultiCultiData2.zip")
# DataIn <- file.path("..", "Data", "RawData", "MultiCultiData3.zip")

>>>>

It tidies and organizes the data. It uses a pivot_wider and
interpolation approach to get the Actinic_par and OD values in line
rowwise. This requires careful 'arrange' of the rows. It imports a
metadata catalog (Data/RawData/"CultureCatalog.Rds") and merges the metadata with the imported data based
upon shared values for the variables 'MC', 'Tube', and 'Filename' which
should unambiguously identify a given growth trajectory measured at
OD680 or OD720.

@@

# Multicultivator data files are too large to upload in a single .zip therefore 3 .zipped folders are uploaded. Uncomment the 'DataIn' line with the folder name containing the intended files for import.   
 # DataIn <- file.path("..", "Data", "RawData", "MultiCultiData1.zip")
DataIn <- file.path("..", "Data", "RawData", "MultiCultiData2.zip")
# DataIn <- file.path("..", "Data", "RawData", "MultiCultiData3.zip")
